\bf Landslide: \\ Systematic Dynamic Race Detection in Kernel Space

### 2012-05-18 conclusion.tex
minor updates

We hope that the ideas presented here serve as stepping stones to develop more sophisticated systematic debugging techniques for kernel-level race conditions.
}

@@

\begin{quote}
\em
And lo, the Author did{\s}t pre{\s}ent Land{\s}lide to yon re{\s}earch Community, and to the {\s}tudents of XV-CDX as well. Verily, the Kernel developers young and olde found Bugges of Concurren{\s}y in their code. The {\s}oftware then{\s}eforth worked as Intended, cra{\s}hing nevermore, and there was much rejoicing.
\end{quote}

>>>>

We hope that the ideas presented here serve as stepping stones for future development of more sophisticated systematic debugging techniques for kernel-level race conditions.
}

@@

%\begin{figure}[p]
\begin{quote}
\em
And lo, the Author did{\s}t pre{\s}ent Land{\s}lide to yon re{\s}earch Community, and to the {\s}tudents of XV-CDX as well. Verily, the Kernel developers young and olde found Bugges of Concurren{\s}y in their code. The {\s}oftware then{\s}eforth worked as Intended, cra{\s}hing nevermore, and there was much rejoicing.
\end{quote}
%\end{figure}

### 2012-05-18 futurework.tex
remove some todos and fixmes
minor updates

% TODO: make visualisations for both of these
\subsection{``Backwards'' Exploration}
\label{sec:future-backwards}

@@

Despite the two trees having nearly equal numbers of branches and instructions executed per branch, \texttt{double\_wait} took significantly more time. This is because Landslide's backtracks during \texttt{double\_wait} were significantly {\em longer} than the backtracks in \texttt{vanish\_vanish} on average; i.e., the backtracks were targetting an earlier point during the test's execution.
Hence, Landslide had to execute more total instructions overall to explore the longer branches in \texttt{double\_wait}.\footnote{
Of note, if backtracking had been implemented by restarting the test each time; i.e., executing the full depth of every branch from the root of the tree, the repeated work would have caused the execution times to be equal. The fact that Simics's backtracking avoids the cost of execution that happened before the backtrack target is to credit for this discrepancy.}
We show an exaggerated visualisation of this tree structure in Figure~\ref{fig:nadim}

\begin{figure}[h]
	\centering
	\includegraphics[width=0.9\textwidth]{nadim.pdf}
	\caption{Though the execution trees in \texttt{double\_wait} and in \texttt{vanish\_vanish} had the same number of branches, with each approximately as many instructions deep, the backtracks in \texttt{double\_wait} were much longer, resulting in more {\em total} instructions executed during the exploration.}
	\label{fig:nadim}
\end{figure}

>>>>

\subsection{``Backwards'' Exploration}
\label{sec:future-backwards}

@@

Despite the two trees having nearly equal numbers of branches and instructions executed per branch, \texttt{double\_wait} took significantly more time. This is because Landslide's backtracks during \texttt{double\_wait} were significantly {\em longer} than the backtracks in \texttt{vanish\_vanish} on average; i.e., the backtracks were targetting an earlier point during the test's execution.
Hence, Landslide had to execute more total instructions overall to explore the longer branches in \texttt{double\_wait}.\footnote{
Of note, if backtracking had been implemented by restarting the test each time; i.e., executing the full depth of every branch from the root of the tree, the repeated work would have caused the execution times to be equal. The fact that Simics's backtracking avoids the cost of execution that happened before the backtrack target is to credit for this discrepancy.}
\revision{We show an exaggerated visualisation of this tree structure in Figure~\ref{fig:nadim}.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.9\textwidth]{nadim.pdf}
	\caption{Though the execution trees in \texttt{double\_wait} and in \texttt{vanish\_vanish} had the same number of branches, with each approximately as many instructions deep, the backtracks in \texttt{double\_wait} were much longer, resulting in more {\em total} instructions executed during the exploration.}
	\label{fig:nadim}
\end{figure}
}
